---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # , fig.path = "vignettes/readme_figs/"
```

[![version](http://www.r-pkg.org/badges/version/groupFusedMulti)](https://cran.r-project.org/package=groupFusedMulti)
<!-- [![Build Status](https://travis-ci.org/jaredhuling/vennLasso.svg?branch=master)](https://travis-ci.org/jaredhuling/groupFusedMulti) -->

# groupFusedMulti

The `groupFusedMulti` package provides methods for hierarchical variable selection for models with covariate effects stratified by multiple binary factors.




## Installation and Help Files

<!-- The `groupFusedMulti` package can be installed from CRAN using: -->
<!-- ```{r, eval = FALSE} -->
<!-- install.packages("groupFusedMulti") -->
<!-- ``` -->

The development version can be installed using the **devtools** package:

```{r, eval = FALSE}
devtools::install_github("jaredhuling/groupFusedMulti")
```


or by cloning and building.

Load the **groupFusedMulti** package:
```{r, warning=FALSE, message=FALSE}
library(groupFusedMulti)
```

Access help file for the main fitting function ``groupFusedMulti()`` by running:

```{r, eval = FALSE}
?groupFusedMulti
```

Help file for cross validation function ``cv.groupFusedMulti()`` can be accessed by running:

```{r, eval = FALSE}
?cv.groupFusedMulti
```

## A Quick Example

Simulate multivariate response data where the responses have a natural grouping:

```{r}
set.seed(123)

dat.sim <- gen_sparse_multivar_data(nvars = 10L,
                   noutcomes = 8L, ## 8-dim response vector
                   nobs = 100L,
                   num.nonzero.vars = 5,
                   outcome.groups = rbind(c(1,1,1,2,2,2,2,2),
                                          c(1,1,1,2,2,3,3,3)))

# design matrices
x        <- dat.sim$x
x.test   <- dat.sim$x.test

# response vectors
y        <- dat.sim$y
y.test   <- dat.sim$y.test

# true data-generating coefficients
beta     <- rbind(0,dat.sim$beta)

outcome_groups <- rbind(c(1,1,1,2,2,2,2,2),
                        c(1,1,1,2,2,3,3,3))

```

First fit a model for a range of tuning parameter values (no cross validation perfomed here)

```{r}
fit.gfm <- groupFusedMulti(x, y,
                           nlambda        = 25,
                           lambda.fused = c(0.00001, 0.0001, 0.001),
                           outcome.groups = outcome_groups,
                           adaptive.lasso = TRUE, adaptive.fused = TRUE,
                           gamma          = 0.5)
```

Plot coefficient paths for the second response/outcome across all variables for the second fused lasso tuning parameter: 

```{r, eval = TRUE}
plot(fit.gfm, lam.fused.idx = 2,
     which.outcome = 2)
```

Plot coefficient paths for a single variable across all outcomes for the second fused lasso tuning parameter: 

```{r, eval = TRUE}
plot(fit.gfm, lam.fused.idx = 2,
     plot.type = "all_outcomes",
     which.variable = 1, ## plot for first variable
     which.outcome.group = 2) ## color according to second grouping
```

Fit `groupFusedMulti` model with tuning parameter selected with 5-fold cross validation:

```{r}
cvfit.gfm <- cv.groupFusedMulti(x, y,
                                nlambda        = 50,
                                lambda.fused = c(0.000005, 0.00001, 0.000025, 0.00005, 0.0001),
                                outcome.groups = outcome_groups,
                                adaptive.lasso = TRUE, adaptive.fused = TRUE,
                                gamma          = 0.5,
                                nfolds         = 5)
```



Compare estimated with true coefficients
```{r}
est.coefs <- predict(cvfit.gfm, type = "coef")
colnames(beta) <- colnames(est.coefs)
rownames(beta) <- rownames(est.coefs)

round(est.coefs, 3)
beta
```


Predict response for test data:

```{r}
preds.gfm <- predict(cvfit.gfm, x.test, type = 'response')
str(preds.gfm)
```

Evaluate mean squared error for each outcome:

```{r}
sqrt(colMeans((y.test - preds.gfm) ^ 2))
```

Average MSE across the 8 outcomes:
```{r}
mean(sqrt(colMeans((y.test - preds.gfm) ^ 2)))
```




